Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
Add clarification for @danysk

The system is composed of two kinds of device: \emph{wearable} and \emph{alert}.
%
Wearables consist of the following pulverised components:
sensors ($\sigma^w$), perceiving other devices by their signal strenght;
behaviour ($\beta^w$), converting raw data from the sensor into messages for the alert system; and
communication ($\chi^w$) sending data to the alert system.
%
They do not need state nor actuators.
%
The alert consists of the following pulverized components:
$\beta^a$, computing the mean distance among devices;
$\kappa^a$ \meta{
    NICOLAS what does this do? write within this meta block
};
$\chi^a$, responsible for receiving the data from the wearable devices;
$\alpha^a$, enacting the alarm by showing a color on the screen.
%
It needs no sensors.

@@

The initial deployment of the system starts with the $\beta_{werable}$ executed in the \emph{Server},
the $\sigma_{wearable}$ and $\chi_{werable}$ executed in the \emph{Smartphones},
and all the \emph{Laboratory} components are executed in the \emph{Local PC}.
%
Given the infrastracture defined above, we simulate also a condition where the \emph{Server} is overloaded and, via pulverization,
we want to lighteninig the load of the \emph{Server} by moving the $\beta_{werable}$ in the \emph{Smartphones}.
%
Formally, we can write the reconfiguration event as follow: $\beta^{werable}_{server} \xrightarrow{\mathcal{E}} \beta^{werable}_{smartphone}$
where $\mathcal{E}$ represents the reconfiguration event due to the high load in the \emph{Server}.

At the start of the system, each \emph{Werable} device, with the $\sigma$ component,
start to perceive the other devices in the laboratory using the RSSI signal from the Bluetooth.
%
The $\beta$ component, initially executed in the \emph{Server}, starts to compute the distances from the other devices
based on the received RSSI signal from the $\sigma$ component.
%
Once the distances are computed, the $\chi$ component sends the data to the
\emph{Laboratory} containing the dinstances perceived by the device.
%

Similarity, the \emph{Laboratory} device has all the components executed in the \emph{Local PC},
where the $\chi$ component receives the data from the \emph{Wearable},
the $\beta$ component computes the mean distance between the devices.
%
The $\kappa$ component persist in memory the updated devices grpah based on the distances retreived by the $\chi$ component.
and the $\alpha$ component show in the monitor the color based on the mean distance computed by the $\beta$ component.

As soon as the reconfiguration event is triggered, the $\beta$ component of the \emph{Werable} is moved from the \emph{Server} to the \emph{Smartphone}
lighteninig the server and preserving from one side the functional semantic of the system and from the other side maintain the system operational.
%
The reconfiguration of the system in entirely managed by the framework, which handle all the machinery and communication to move the component from
one host to another.
%
With this simple example we show how the pulverization framework can be used in practice to manage a system with different devices and an heterogeneous
infrastructure.
%
Moreover, we show how the pulverization framework can be used adapt the system to changing requirement without loosing the funcional semantic of the system
by describing the system in a declarative way.

>>>>

The system is composed of two kinds of device: \emph{wearable} and \emph{alert}.
%
Wearables consist of the following pulverised components:
sensors ($\sigma^w$), perceiving other devices by their signal strength;
behaviour ($\beta^w$), converting raw data from the sensor into messages for the alert system; and
communication ($\chi^w$) sending data to the alert system.
%
They do not need state nor actuators.
%
The alert consists of the following pulverized components:
$\beta^a$, computing the mean distance among devices;
$\kappa^a$ \meta{
    NICOLAS what does this do? write within this meta block.
    %
    Hold in memory the updated distances between the devices.
};
$\chi^a$, responsible for receiving the data from the wearable devices;
$\alpha^a$, enacting the alarm by showing a color on the screen.
%
It needs no sensors.

@@

The initial deployment of the system starts with the $\beta_{werable}$ executed in the \emph{Server},
the $\sigma_{wearable}$ and $\chi_{werable}$ executed in the \emph{Smartphones},
and all the \emph{Laboratory} components are executed in the \emph{Local PC}.
%
Given the infrastructure defined above, we simulate also a condition where the \emph{Server} is overloaded and, via pulverization,
we want to lightening the load of the \emph{Server} by moving the $\beta_{werable}$ in the \emph{Smartphones}.
%
Formally, we can write the reconfiguration event as follow: $\beta^{werable}_{server} \xrightarrow{\mathcal{E}} \beta^{werable}_{smartphone}$
where $\mathcal{E}$ represents the reconfiguration event due to the high load in the \emph{Server}.

At the start of the system, each \emph{Wearable} device, with the $\sigma$ component,
start to perceive the other devices in the laboratory using the RSSI signal from the Bluetooth.
%
The $\beta$ component, initially executed in the \emph{Server}, starts to compute the distances from the other devices
based on the received RSSI signal from the $\sigma$ component.
%
Once the distances are computed, the $\chi$ component sends the data to the
\emph{Laboratory} containing the distances perceived by the device.
%

Similarity, the \emph{Laboratory} device has all the components executed in the \emph{Local PC},
where the $\chi$ component receives the data from the \emph{Wearable},
the $\beta$ component computes the mean distance between the devices.
%
The $\kappa$ component persist in memory the updated devices graph based on the distances retrieved by the $\chi$ component.
and the $\alpha$ component show in the monitor the color based on the mean distance computed by the $\beta$ component.

As soon as the reconfiguration event is triggered, the $\beta$ component of the \emph{Wearable} is moved from the \emph{Server} to the \emph{Smartphone}
lightening the server and preserving from one side the functional semantic of the system and from the other side maintain the system operational.
%
The reconfiguration of the system in entirely managed by the framework, which handle all the machinery and communication to move the component from
one host to another.
%
With this simple example we show how the pulverization framework can be used in practice to manage a system with different devices and an heterogeneous
infrastructure.
%
Moreover, we show how the pulverization framework can be used adapt the system to changing requirement without loosing the functional semantic of the system
by describing the system in a declarative way.
